Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-26 mice_synthesizing/paper.Rmd
Adjusted intro.

@@

Potentially, these approaches could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints. However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data. It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.

>>>>

An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993. Although their approaches differed to some extent, the general concept was to release multiply imputed synthetic datasets, instead of the actually observed data. Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data. The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold. Additionally, a researcher can opt to simply replace all values of every observation.

Potentially, this approach could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints. However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.

The goal then is to release multiply imputed datasets that bear no risk of releasing confidential or identifying information, while the multivariate relationships should be preserved as in the observed data.

The fact that the then released data is synthetic could potentially fulfil the needs for openly accessible data, without running into barriers with regard to privacy and confidentiality constraints.

, based on the multiple imputation framework [@rubin_multiple_1987].

Potentially, these approaches  However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data. It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.

@@
